### 2014-06-22 dicook/map.Rmd

  dframe <- ldply(1:length(shapes@polygons), function(i) {
    ob <- shapes@polygons[[i]]@Polygons
    dframe <- ldply(1:length(ob), function(j) {
      x <- ob[[j]]
      co <- x@coords
      data.frame(co, order=1:nrow(co), group=j)
    })
    dframe$region <- i
    dframe$name <- shapes@polygons[[i]]@ID
    dframe
  })
  # construct a group variable from both group and polygon:
  dframe$group <- interaction(dframe$region, dframe$group)

>>>>

  dframe <- ldply(1:length(shapes@polygons), function(i) {
    ob <- shapes@polygons[[i]]@Polygons
    dframe <- ldply(1:length(ob), function(j) {
      x <- ob[[j]]
      co <- x@coords
      data.frame(co, order=1:nrow(co), group=j)
    })
    dframe$region <- i
    dframe$name <- shapes@polygons[[i]]@ID
    dframe$area <- shapes@polygons[[i]]@area
    dframe
  })
  # construct a group variable from both group and polygon:
  dframe$group <- interaction(dframe$region, dframe$group)
